---
title: "NSForestR"
author: "Shweta Gopaulakrishnan"
date: "4/4/2019"
output: html_document
---

# NSforest in R (via reticulate+python by Aevermann/Scheuermann et al.)

- Our package NSForestR helps work with NS Forest implementation
from https://github.com/JCVenterInstitute/NSForestin in R. 

- We have developed few methods to do this: 

#NSforestR demo native R version of
#https://github.com/JCVenterInstitute/NSForest

- For illustration purposes, we have 
Dataset : Ab10k.tsv -  17-feature dataset for 7k PBMC 

The parameters are define as :
rfTrees: number of trees built in random forest step
threads: number of threads for python execution
Median_Expression_Level: median expression level
InformativeGenes: number of genes to regard as informative for each cluster
Genes_to_testing: number of genes to retain in reporting
betaValue: set values for fbeta weighting

```{r code2}
library(NSForestR)
tsvfile = system.file("data/Ab10k.tsv", package="NSForestR")
chk = NSForestCL(tsvfile, clusterCol=2, clusterValue=2, rfTrees=100, informativeGene=5, num_top_ranked=3, betaValue=0.5, column=2)
chk
```


## Using "reticulate":

```{r code}

tsvfile = system.file("data/Ab10k.tsv", package="NSForestR")
runNSFromPython(tsvfile, rfTrees=100L, threads=1L, Median_Expression_Level=0L, InformativeGenes=5L,
                Genes_to_testing=3L, betaValue=0.5)
```

# Additional Methods 

- To transform a Single Cell Experiment object to tsv file 

```{r example}

data(pcmp::Ab10k)
tf = tempfile(fileext=".tsv")
sceTotsv(Ab10k,tf)
head(read.delim(tf,sep="\t"))

```

